---
title: "RLohiya_Assignment3_PS1&PS2"
author: "Ritesh Lohiya"
date: "September 14, 2018"
output: html_document
---

---
title: "Data605_HW3_PS1"
author: "Ritesh Lohiya"
date: "September 13, 2018"
output: html_document
---

#                             ASSIGNMENT 3

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

#                            Problem set 1

1. What is the rank of the matrix A?

```{r}
rank = 0
A <- matrix(c(1, -1, 0, 5, 2, 0, 1, 4, 3,1 -2, -2,4,3,1,-3), nrow=4, ncol=4) 
A
```

Rank of the matrix using qr function:

```{r}
rank <- qr(A)$rank
rank
```

The rank is 4

2. Given an mxn matrix where m > n, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?

The Matrix can have a maximum rank of rank(A)=n and mininum rank of 1

3. What is the rank of matrix B?

```{r}
B<-matrix(c(1,2,1,3,6,3,2,4,2), byrow =TRUE,nrow = 3,ncol = 3)
qr(B)$rank
```

The rank is 1

#                            Problem set 2

Compute the eigenvalues and eigenvectors of the matrix A. You'll need to show your work. You'll need to write out the characteristic polynomial and show your solution.

```{r}
A <- matrix(c(1, 0, 0, 2, 4, 0, 3, 5, 6), nrow=3, ncol=3)
E_Vals <- eigen(A)
E_Vals
```

The manual work is placed at the below location on Github and will be attached also.

Link for manual work: https://github.com/Riteshlohiya/Data605_HW3/blob/master/RLohiya_Assignment3_PS2.pdf


